%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \namesection{Anubhav}{Tomar}{
\namesection{}{Anubhav Tomar}{
% \urlstyle{same}\url{https://github.com/andypillay} \\
Interest Areas: Web Development, Cloud/Distributed Systems, Embedded Systems, Software Engineering\\
+1-(631)-428-8874 | \href{mailto:anubhav.tomar94@gmail.com}{\color{blue}anubhav.tomar94@gmail.com} | \href{https://anubhavtomar.github.io}{\color{blue}anubhavtomar.github.io} | \href{https://www.linkedin.com/in/anubhav-tomar/}{\color{blue}linkedin@anubhav-tomar} | \href{https://github.com/anubhavtomar}{\color{blue}github@anubhavtomar}
}

% \href{uk.linkedin.com/in/andypillay}{uk.linkedin.com/in/andypillay}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\descbold{JavaScript, Python, SystemC, Assembly, C++, Perl, Ruby, C, HTML5, CSS3, Tcl/Tk, Scripting | NodeJS, AngularJS, EmberJS, MeteorJS, OpenCV, TensorFlow, RoR, Flask, MVC, jQuery, Bootstrap, Android(Kotlin), Cordova, Grunt, NS2 | Git, JIRA, LaTex, Agile}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{Stony Brook University}
\descript{| M.S. Computer Engineering}
\hfill
\location{GPA: 3.58/4.00 | Aug 2018 – Dec 2019}\\
\descbold{Coursework:} Analysis of Algorithms, Computer Vision, Cyber-Physical Systems, Digital System Specification and Modeling, Hardware-Software Co-Design of Embedded Systems, Wireless Network, Computer-Aided Design, Modern Sensors.\\
\sectionsep
\runsubsection{NSIT (University of Delhi)}
\descript{| B.E. Control Engineering}
\hfill
\location{GPA: 7.46/10.00 | Aug-2011 - May 2015}\\
\descbold{Coursework:} Computer Networks, Computer Graphics, Data Structures, Microprocessors, Digital Signal Processing.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Stony Brook University}
\descript{| Graduate Teaching Assistant}
\hfill
\location{ Spring 2019 | Stony Brook, NY}\\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Serving as a Teaching Assistant and grader for the undergraduate course - ESE 344 Software Techniques for Engineers (C++ programming) under Prof. Murali Subbarao.
\end{tightemize}
\sectionsep

\runsubsection{Homebell}
\descript{| Software Engineer}
\hfill
\location{ Mar 2017 – Aug 2018 | Noida, India}\\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \descbold{Emma:} Designed \& developed a SaaS for subcontractor companies in Germany using AngularJS 2 and RoR.
\item Responsible for frontend (AngularJS) and backend (RoR) for feature development across different products.
\end{tightemize}
\sectionsep

\runsubsection{Oravel Stays (OYO)}
\descript{| Software Engineer}
\hfill
\location{ Mar 2016 – Mar 2017 | Gurugram, India}\\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \descbold{Owner App:} Built a hybrid application using EmberJS, Cordova on front-end \& RoR on back-end. Used by OYO owners.
\item \descbold{Lifeline:} Designed \& developed internal web portal. Used by customer service center and administrators.
\end{tightemize}
\sectionsep

\runsubsection{TravelClinic}
\descript{| Software Intern}
\hfill
\location{ Oct 2015 – Mar 2016 | Noida, India}\\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed \& developed a social networking web application from scratch using MeteorJS.\descbold{ Features:} Recommendations for the nearby restaurants and events, Chat, \& 2 player Tic-Tac-Toe game.
\end{tightemize}
\sectionsep

\runsubsection{Defense R\&D Organisation, Govt. of India}
\descript{| Summer Intern}
\hfill
\location{ Summer 2014 | Hyderabad, India}\\
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built a GUI using Python for serially communicating (RS 232 channel) with Altimeter and proprietary GPS Receiver. The data is used for evaluation and calibration of the Altimeter.
\end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{RISC Processor Architecture with 5-Stage Pipeline Execution}
\descbold{| SystemC}
\hfill
\location{\href{https://github.com/anubhavtomar/ESE501}{\color{blue}github@ESE501}}\\
RTL Level Modeling of a 16-bit RISC Processor. 5 stages: Instruction Fetch, Decode, ALU/EXE, Memory Access \& Write Back.
\sectionsep

\runsubsection{Gesture Recognition using Acoustics}
\hfill
\location{\href{https://github.com/anubhavtomar/gesture-app}{\color{blue}github@gesture-app}}\\
\descbold{Android, Deep Learning, CNN, Tensor Flow, Python, Flask, Signal Processing}\\
An Android application for detecting hand gestures ('Open Fist' / 'Closed Fist') using high-frequency acoustic waves.
\sectionsep

\runsubsection{Sound Controlled Stopwatch}
\descbold{| PSoC1, Assembly}
\hfill
\location{\href{https://github.com/anubhavtomar/psoc-stopwatch}{\color{blue}github@psoc-stopwatch}}\\
An implementation of a Stopwatch on PSoC1. The stopwatch works for Sound inputs and Push Button inputs.
\sectionsep

\runsubsection{Simulated Annealing Algorithm in Mixed Signal Processing}
\descbold{| C++, Perl}
\hfill
\location{\href{https://github.com/anubhavtomar/annealing-partitioning}{\color{blue}github@annealing-partitioning}}\\
An implementation of \location{\href{https://link.springer.com/article/10.1023/A:1008857008151}{\color{blue}Hardware/Software Partitioning
based on Simulated Annealing}} for Fast Fourier Transform (FFT).
\sectionsep

\runsubsection{Simulation of Routing algorithms for VANET}
\descbold{| Tcl/Tk, NS2}
\hfill
\location{B.E Final Year Project}\\
Simulated VANET routing protocols AODV (Ad Hoc On-Demand Distance Vector) and DSDV(Destination-Sequenced Distance-Vector Routing) using Network Simulator (NS2) for an on-demand Traffic communication.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{ACHIEVEMENTS \& EXTRACURRICULAR}
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% \descbold{Professional} & OYO-Person of Contact, Owner App\\
% & Defense R\&D Organisation-Project Head in a team size of 4\\
% \descbold{Online Courses} & Machine Learning A-Z\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Skills}
% \begin{minipage}[t]{.6\textwidth}
% \subsection{Languages}
% \location{Proficient:}
% C\# \textbullet{} Python \textbullet{} CSS \textbullet{} HTML \textbullet{} MSSQL \\ 
% \location{Familiar/Studying:}
% JavaScript \textbullet{} Scala \textbullet{} C++ 
% \sectionsep
% \end{minipage}
% \hfill
% \begin{minipage}[t]{.35\textwidth}
% \subsection{Spoken \& Written}
% \location{Native fluency:} English\\
% \location{Working proficiency:} French Creolé\\
% \end{minipage}

% \begin{minipage}[t]{.6\textwidth}
% \subsection{Frameworks }
% .NET \textbullet{} jQuery \textbullet{} Bootstrap \textbullet{} Django \textbullet{} Entity\\
% \end{minipage}
% \hfill
% \begin{minipage}[t]{.35\textwidth}
% \subsection{Software / Version Control}
% Terminal \textbullet{} Git \textbullet{} Team Foundation Server \\ 
% \end{minipage}
% \hfill

% \begin{minipage}[t]{.6\textwidth}
% \subsection{Methodologies / Practices }
% Agile \textbullet{} Scrum \textbullet{} Test Driven Development \\
% \end{minipage}
% \hfill
% \begin{minipage}[t]{.35\textwidth}
% \subsection{IDE's / Text Editors }
% Visual Studio \textbullet{} Sublime Text \textbullet{} Notepad++ \\ 
% \end{minipage}

\vfill
Last Updated on \today
\hfill 
Visa Status: F1 Holder
% \lastupdated
\end{document}  

\documentclass[]{article}